### 2023-07-10 README.Rmd
Vasrious updates. Now us refperiodCE in hsargs instead of startCE and endCE.

>>>>

* 2023-07-10 aMSE 0.1.6 Modified TasHS and aMSE so that instead of using hsargs$startCE and hsargs$endCE to define a vector of reference years when using the constantrefhcr in Tasmania, one should now use a hsargs$refperiodCE which should be a vector of years describing the constant reference period to be used (assuming one is using the constantrefhcr). Within TasHS there is also a checkhsargs() function which provides a brief check of the hsargs being used (strictly that is still under development).
